## Basic Scatterplot

```{r, eval = FALSE}
library(plotly)
plot_ly(mtcars, x = mtcars$wt, y = mpg, mode = "markers")
```


## Scatterplot Color

```{r, echo = FALSE, message = FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mpg, mode = "markers", color = as.factor(mtcars$cyl))
```

## Continuous Color

You can also show continuous variables with color in scatterplots.

```{r, eval = FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mpg, mode = "markers", color = mtcars$disp)
```

## Continuous Color

```{r, echo = FALSE, message=FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mtcars$mpg, mode = "markers", color = mtcars$disp)
```

## Scatterplot Sizing

By specifying the `size` argument you can make each point in yout scatterplot a different size.

```{r, eval = FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mtcars$mpg, mode = "markers", color = as.factor(mtcars$cyl),
        size = mtcars$hp)
```


## 3D Scatterplot

You can create a three-dimensional scatterplot with the `type = "scatter3d"` argument. If you click and drag these scatterplots you can view them from different angles.
```{r}
set.seed(2016-07-21)
temp <- rnorm(100, mean = 30, sd = 5)
pressure2 <- rnorm(100)
dtime <- 1:100
plot_ly(x = temp, y = pressure2, z = dtime, 
        type = "scatter3d", mode = "markers", color = temp)
```


## Line Graph 

```{r, eval = FALSE, message=FALSE}
data("airmiles")
plot_ly(x = time(airmiles), y = airmiles, type = "bar")
```

## Multi line Graph

You can show multiple lines by specifying the column in the data frame that separates the lines:
```{r}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")

stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
# problematic
plot_ly(stocks, x = EuStockMarkets$time, y = EuStockMarkets$price, color = index)
```
